Highly Available Transactions: Virtues and Limitations

### 2013-03-31 writeup/motivation.tex
References purge

Several recent studies rigorously quantify partition behavior. A 2011
study of several Microsoft datacenters found a mean of 40.8 network
link failures per day (95th percentile: 136), with a median time to
repair of around five minutes (and up to one week). Perhaps
surprisingly, provisioning redundant networks only reduces impact of
failures by up to 40\%, meaning network providers cannot easily
curtail partition behavior~\cite{sigcomm-dc}. A 2010 study of over 200
wide-area routers found an average of 16.2--302.0 failures per link
per year with an average annual downtime of 24--497 minutes per link
per year (95th percentile at least 34 hours)~\cite{sigcomm-wan}. In
HP's managed enterprise networks, WAN, LAN, and connectivity problems
account for 28.1\% of all customer support tickets while 39\% of
tickets relate to network hardware.  The median incident duration for
highest priority tickets ranges from 114--188 minutes and up to a full
day for all tickets~\cite{turner2012failure}. Other studies confirm
these results, showing median time between failures over a WAN network
of approximately 3000 seconds with a median time to repair between 2
and 1000 seconds~\cite{ip-backbone-failures} as well as frequent path
routing failures on the Internet~\cite{labovitz-failures}. Isolating,
quantifying, and designing for these network failures is an area of
active research in networking
community~\cite{surviving-failures-bodik, uw-failure-networks}.

These results---which do not consider server-level failures (another
form of system partition that has also been studied at
scale~\cite{google-availability})---indicate that network partitions
\textit{do} occur within and across modern datacenters. We do not
intend to fixate on any particular statistical behavior but instead
observe that, as a general trend, partitions exist and must
accordingly be met with either unavailability at some servers or, as
we will discuss, relaxed semantic guarantees.

@@

In real deployments, transit times are actually slower than the speed
of light due to routing, congestion, and processing times. To
illustrate the difference between intra-datacenter, inter-datacenter,
and inter-planetary networks, we performed a measurement study of
network behavior on Amazon's EC2, a widely-used public compute
cloud. We measured one week of ping times between all seven EC2
geographic ``regions'', across three ``availability zones'' (closely
co-located datacenters), and within a single ``availabilty zone''
(datacenter), at a granularity of 1s (dataset to be released). We
summarize the results of our network measurement study in
Table~\ref{table:rtt}. On average, intra-datacenter communication (1a)
is between 1.82 and 6.38 times faster than across geographically
co-located datacenters (1b) and between 40 and 647 times faster than
across geographically distributed datacenters (1c). The cost of
wide-area communication exceeds the speed of light: for example,
communicating from S\~{a}o Paulo to Singapore is lower-bounded by
speed-of-light transit RTT of 106.7ms but, on average, incurs a
362.8ms RTT (95th percentile: 649ms). As shown in
Figure~\ref{fig:rtt}, the distribution of latencies varies between
links, but the trend---in line with other recent studies~\cite{mdcc,
  redblue}---is clear: remote communication has a substantial cost.

>>>>

Several recent studies rigorously quantify partition behavior. A 2011
study of several Microsoft datacenters found a mean of 40.8 network
link failures per day (95th percentile: 136), with a median time to
repair of around five minutes (and up to one week). Perhaps
surprisingly, provisioning redundant networks only reduces impact of
failures by up to 40\%, meaning network providers cannot easily
curtail partition behavior~\cite{sigcomm-dc}. A 2010 study of over 200
wide-area routers found an average of 16.2--302.0 failures per link
per year with an average annual downtime of 24--497 minutes per link
per year (95th percentile at least 34 hours)~\cite{sigcomm-wan}. In
HP's managed enterprise networks, WAN, LAN, and connectivity problems
account for 28.1\% of all customer support tickets while 39\% of
tickets relate to network hardware.  The median incident duration for
highest priority tickets ranges from 114--188 minutes and up to a full
day for all tickets~\cite{turner2012failure}. Other studies confirm
these results, showing median time between failures over a WAN network
of approximately 3000 seconds with a median time to repair between 2
and 1000 seconds~\cite{ip-backbone-failures} as well as frequent path
routing failures on the Internet~\cite{labovitz-failures}. Isolating,
quantifying, and designing for these network failures is an area of
active research in networking
community~\cite{uw-failure-networks}.

These results---which do not even consider server-level
failures---indicate that network partitions \textit{do} occur within
and across modern datacenters. We do not intend to fixate on any
particular statistical behavior but instead observe that, as a general
trend, partitions exist and must accordingly be met with either
unavailability at some servers or, as we will discuss, relaxed
semantic guarantees.

@@

In real deployments, transit times are actually slower than the speed
of light due to routing, congestion, and processing times. To
illustrate the difference between intra-datacenter, inter-datacenter,
and inter-planetary networks, we performed a measurement study of
network behavior on Amazon's EC2, a widely-used public compute
cloud. We measured one week of ping times between all seven EC2
geographic ``regions'', across three ``availability zones'' (closely
co-located datacenters), and within a single ``availabilty zone''
(datacenter), at a granularity of 1s (dataset to be released). We
summarize the results of our network measurement study in
Table~\ref{table:rtt}. On average, intra-datacenter communication (1a)
is between 1.82 and 6.38 times faster than across geographically
co-located datacenters (1b) and between 40 and 647 times faster than
across geographically distributed datacenters (1c). The cost of
wide-area communication exceeds the speed of light: for example,
communicating from S\~{a}o Paulo to Singapore is lower-bounded by
speed-of-light transit RTT of 106.7ms but, on average, incurs a
362.8ms RTT (95th percentile: 649ms). As shown in
Figure~\ref{fig:rtt}, the distribution of latencies varies between
links, but the trend is clear: remote communication has a substantial
cost.

### 2013-03-31 writeup/relatedwork.tex
References purge

There has been a recent resurgence of interest in distributed
multi-object semantics, both in academia~\cite{kraska-s3, granola,
  gstore, mdcc, redblue, cops, eiger, walter,calvin, swift} and
industry~\cite{megastore, orleans, spanner}. As discussed in
Section~\ref{sec:modernacid}, classic ACID databases provide strong
semantics but their lock-based and traditional multi-versioned
implementations are unavailable in the presence of
partitions~\cite{bernstein-concurrency, bernstein-book,
  gray-isolation}. Notably, Google's Spanner provides strong one-copy
serializable transactions. While Spanner is highly specialized for
Google's read-heavy workload, it relies on two-phase commit and
two-phase locking for read/write transactions~\cite{spanner}. As we
have discussed, the latency penalties associated with this design
choice are fundamental to serializability. For users willing to
tolerate these costs, Spanner, or similar strongly consistent,
unavailable systems---including Calvin~\cite{calvin},
G-Store~\cite{gstore}, Gemini~\cite{redblue}, Generalized Snapshot
Isolation~\cite{generalizedsnapshot}, Granola~\cite{granola},
HBase, MDCC~\cite{mdcc}, Megastore~\cite{megastore},
Orleans~\cite{orleans}, Postgres-R~\cite{kemme-thesis},
Walter~\cite{walter}, and a range of snapshot isolation
techniques~\cite{middleware-db, kemme-snapshot,
  daudjee-snapshot}---are a reasonable choice.

>>>>

There has been a recent resurgence of interest in distributed
multi-object semantics, both in academia~\cite{kraska-s3, granola,
  gstore, mdcc, eiger, walter,calvin, swift} and
industry~\cite{orleans, spanner}. As discussed in
Section~\ref{sec:modernacid}, classic ACID databases provide strong
semantics but their lock-based and traditional multi-versioned
implementations are unavailable in the presence of
partitions~\cite{bernstein-book, gray-isolation}. Notably, Google's
Spanner provides strong one-copy serializable transactions. While
Spanner is highly specialized for Google's read-heavy workload, it
relies on two-phase commit and two-phase locking for read/write
transactions~\cite{spanner}. As we have discussed, the latency
penalties associated with this design choice are fundamental to
serializability. For users willing to tolerate these costs, Spanner,
or similar strongly consistent, unavailable systems---including
Calvin~\cite{calvin}, G-Store~\cite{gstore}, Generalized Snapshot
Isolation~\cite{generalizedsnapshot}, HBase, HStore~\cite{hstore},
MDCC~\cite{mdcc}, Orleans~\cite{orleans},
Postgres-R~\cite{kemme-thesis}, Walter~\cite{walter}, and a range of
snapshot isolation techniques~\cite{middleware-db, kemme-snapshot,
  daudjee-snapshot}---are a reasonable choice.
